Photovoltaic System Reconfiguration strategy for mismatch condition\\ {\footnotesize \textsuperscript{}}

### 2018-08-26 main.tex
Modify Version - 1.0
modify paper
add figure
missing test data, last figure

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
%% \usepackage{subfigure}
\usepackage{subfig}
%% \usepackage{subcaption}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Photovoltaic System Reconfiguration strategy for mismatch condition\\
{\footnotesize \textsuperscript{}}}

@@

\section{Assumption of a PV array} \label{assum}
In this paper, we use the following definitions of PV arrays, modules, strings and panels as showed in Fig. \ref{fig1}. A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels. For a PV panel, formed by three PV modules connected in series with bypass diodes. 
\begin{figure}[htbp]
\centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
\caption{PV arrays, strings, and panels.}
\label{fig1}
\end{figure}

@@

\section{Reconfiguration Algorithm} \label{algo}
As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}. Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates. Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array. Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations. The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}.

\subsection{Feasibility}
The feasibility of configuration based on the assumption of section \ref{assum}, each string in PV array must have same number of panels. Definition of feasibility in (\ref{feas}). When a configuration needs panels in a string (\textit{$NP_n$}) are over mean value for number of panels per-string this configuration is unfeasible. 
\begin{equation}
\left\{\begin{matrix}
NP_n > NP\div N_{st}& & \text{Unfeasible}\\ 
NP_n \leq NP\div N_{st} & & \text{Feasible} 
\label{feas}
\end{matrix}\right. 
\end{equation}

\begin{table}[htbp]
\caption{}
\begin{center}
\begin{tabular}{cccc}
\multicolumn{4}{c}{DATA OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}0, 22.8, 22.8{]}    \\
P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\subsection{Reconfiguration strategy}
Based on existed reconfiguration
%The general steps of reconfiguration algorithm are presented in Fig. \ref{fig2}. The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array. When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}. For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal. For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules (\textit{$N_a$}) by average MPP voltages (\textit{$\bar V_{mpp}$}) with $\pm$18\% error \cite{b10}. Afterward, determine real number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates by applying method in \cite{b10}. Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}. Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shading distribution among PV array.  Then grouping panels into different shadow distribution.

After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group. However, if just simply grouping panels by shadow distribution conditions it may cause electrical connection overhead or unable calculate optimal configuration. To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
\begin{itemize}
\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
\end{itemize}
\begin{figure}[htbp]
\centerline{\includegraphics[width=6.2cm]{paper-fig3.png}}
\caption{An example of un-uniform shadowed PV array.}
\label{fig3}
\end{figure}

This algorithm will better understood by applying to shadow condition showed in Fig. \ref{fig3}. This PV system is composed with 9 PV panels connected into 3 strings as showed in Fig.\ref{fig3}. Irradiance levels, \textit{$I_{mpp}$} and \textit{$V_{mpp}$} of each module are given in Table \ref{tab1}.

%\begin{table}[]
%\begin{tabular}{cccc}
%\multicolumn{4}{c}{Data of partial-shading PV array} \\
%\\ \hline \hline
%Panels   & Vmpp(V)  & Impp (A)             & MPP(w)  \\ \hline
%P1       &          & {[}0, 0.5, 2{]}      &         \\
%P2       &          & {[}0.5, 3, 3{]}      &         \\
%P3       &          & {[}0.5, 0.5, 0.5{]}  &         \\
%P4       &          & {[}0, 2, 2{]}        &         \\
%P5       &          & {[}0, 0.5, 2{]}      &         \\
%P6       &          & {[}0.5, 2, 2{]}      &         \\
%P7       &          & {[}0.5, 2, 3{]}      &         \\
%P8       &          & {[}2, 2, 2{]}        &         \\
%P9       &          & {[}0.5, 2, 3{]}      &        
%\end{tabular}
%\end{table}

The example refer to a three-strings PV array, each string contain with 3 panels, each one made of three identical PV modules (\textit{N}=3). In this example, it is assumed that input range of DC-DC converter and MPPT device defined by \textit{$V_{min}$} = 200V and \textit{$V_{max}$} = 500V. MPP current candidates and MPP voltage candidates are present in ( \ref{e1} ) and ( \ref{e2} ), respectively. Additional, number of real working module at MPP current candidates are given in ( \ref{e3} ).
\begin{equation}
\begin{aligned}
\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned}
\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned}
\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
\end{aligned}
\end{equation}

\begin{figure}[htbp]
\centerline{\includegraphics[width=8cm]{paper-fig4.png}}
\caption{Organized PV array after first part of Algorithm.}
\label{fig4}
\end{figure}

Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%. Though procedure of algorithm, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]. And PV array are organized as Fig.\ref{fig4}
Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead. In order to reduce electrical connection simulation time, replacement and feasibility check will be approved.

Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string. Firstly, selecting panels for high current string, string three. According to Table \ref{tab1}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A. Those four panel can provide 4 PV module working at 3A and meet requirement of \textit{$Q_{M_n}$}. Because on extra panel can provide module  working on 3A, no replacement will be approved. Means no further improvement for configuration of string three.
Then select panel for string two, Panel 4 and Panel 8 will be selected, but this configuration is not optimized. Selected panels provide 5 modules able to work at 2A, satisfy requirement of \textit{$Q_{M_n}$} $\ge$ 4, but one module more than requirement. The process will replace Panel 4 by Panel 1 that provide just 4 modules working at 2A. Configuration for string two are Panel 8 and Panel 1. At last, select panels for string one. Panel 4, Panel 5, Panel 6 are selected, they can provide 5 modules working at 2A that satisfy requirement. For configuration on string one due to it is the last string to process and meet requirement, in order to reduce computing time replacement will not be approved. Configuration of MPP candidate \{2, 2, 3\} are \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}. As described in section \ref{assum}, each string have identical length and Panel 3 not been used in any configuration. So optimized configuration for this MPP candidate are: \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8, Panel 3\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}. The MPP values of this configuration calculated by multiplay string voltage and current equal to 347.2W are put into evidence.

For the third MPP candidate, as same calculating procedure as fourth MPP candidate, optimized configuration for MPP candidate \{2, 2, 2\} are: \textit{St} 1:\{Panel 4,Panel 8, Panel 3\}, \textit{St} 2: \{Panel 1, Panel 2, Panel 6\}, \textit{St} 3: \{Panel 5, Panel 7, Panel 9\}.

The first MPP candidate \{0.5, 0.5, 2\}, after replacement string three contain four panels, \{Panel 4, Panel 8, Panel 1, Panel 2\} but it is over maximum string length of this PV array.
Also for MPP candidate \{0.5, 2, 2\}, there are no configuration can't provide 7 modules working 
on three different string at 0.5A, 2A, 2A, respectively.

\section{evaluation of optimization algorithm}
%\subsection{Verification of the Proposed algorithm}
This section verifies the effectiveness of proposed algorithm using LTspice simulation. With pilot example presented in last section, shading scenario as showed in Fig.\ref{fig5a}. To minimize power loss, the proposed algorithm, as described, is applied to reconfigure the system. The resulting configuration is depicted in Fig.\ref{fig5b} and Fig.\ref{fig5c}. 
\begin{figure}
\centering

\subfloat[]{
	\label{fig5a}
	\includegraphics[width=5cm]{paper-fig5(a).png} } \\
\subfloat[]{
	\label{fig5b}
	\includegraphics[width=5cm]{paper-fig5(b).png} } \\
\subfloat[]{
	\label{fig5c}
	\includegraphics[width=5cm]{paper-fig5(c).png}} \\
\caption{The PV system under shading scenario (a) before reconfiguration, (b) after reconfiguration for MPP candidate \{2, 2, 3\} and (c) MPP candidate \{2, 2, 2\}} 
\end{figure}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Photovoltaic System Reconfiguration strategy for mismatch condition\\
{\footnotesize \textsuperscript{}}}

@@

\section{Assumption of a PV array} \label{assum}
In this paper, we use the following definitions of PV arrays, modules, strings and panels as showed in Fig. \ref{fig1}. A PV array is formed by several parallel connected (PV) strings, and a string is formed by several series-connected PV panels. For a PV panel, formed by three PV modules (\textit{$N_M=3$}) connected in series with bypass diodes. 
\begin{figure}[htbp]
\centerline{\includegraphics[width=7.2cm]{paper-fig1.png}}
\caption{PV arrays, strings, and panels.}
\label{fig1}
\end{figure}

@@

\section{Reconfiguration Algorithm} \label{algo}
To reconfigure a large scale partial shading PV array, an example refers to 9 panels which have been connected in 3 strings. In this example, mismatching conditions presented in Table \ref{tab1}. Each panel made of 3 identical PV modules (\textit{N=3}), dataset in Table \ref{tab1} are provide by method in \cite{b6} \cite{b7}. As described in \cite{b10}, the Fast reconfiguration strategy firstly determine \textit{$V_{mpp}$} and \textit{$I_{mpp}$} for each PV module by using the algorithm in \cite{b7} \cite{b9}. Then determine MPP current and voltage candidates among PV array. Calculate MPP candidates matrix by multiplying the current and voltage candidates. Using the number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates to determine MPP candidates. Finally the Fast reconfiguration strategy gives MPP candidates for reconfiguration, which specifies a current value and minimum number of working modules for each string in PV array. The general steps of Fast reconfiguration strategy as showed in Fig. \ref{flowchart}. Due to a PV panel can not be used into different string, those MPP candidates may have some un-feasible configurations. Our proposed algorithm based on the method in \cite{b10} to calculate MPP candidates and using unique panel selection technology to give optimal reconfiguration solution among partial-shading PV array.

In this example, though the procedure in Fast reconfiguration strategy, MPP candidates are presented in (\ref{mpp}) and number of working modules in MPP candidates are presented in (\ref{qmn}), respectively.

\begin{table}[htbp]
\caption{}
\begin{center}
\begin{tabular}{cccc}
\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}0, 22.8, 22.8{]}    \\
P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}0, 1.5, 22.8{]}     \\
P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{equation}
\begin{aligned}
\textit{MPP candidates} = [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}]
\end{aligned}\label{mpp}
\end{equation}
\begin{equation}
\begin{aligned}
\textit{$Q_{M_n}$} = &  [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]
\end{aligned}
\label{qmn}
\end{equation}

\subsection{Feasibility}
The feasibility of configuration based on the assumption of section \ref{assum}, each string in PV array must have same number of panels. Definition of feasibility in (\ref{feas}). When a configuration needs panels in a string (\textit{$NP_n$}) are over maximum number of panels per-string(\textit{$NP_{stMAX}$}) this configuration is unfeasible. 
\begin{equation}
\left\{\begin{matrix}
NP_n > NP_{stMAX}& & \text{Unfeasible}\\ 
NP_n \leq NP_{stMAX} & & \text{Feasible} 
\label{feas}
\end{matrix}\right. 
\end{equation}
For the first MPP candidate \{0.5, 0.5, 2\} need 8 modules for each string. According to Table \ref{tab1}, for a string current on 2A at least need 4 panels and didn't meet feasible requirement, thus, algorithm terminate. The second MPP candidate \{0.5, 2, 2\} as same as previous one also not feasible.

\subsection{Panel Selection Strategy} \label{selection strategy}
%Calculate MPP candidates based on existed reconfiguration method in \cite{b10}. MPP current candidates and MPP voltage candidates are present in (\ref{e1}) and (\ref{e2}), respectively. Additional, number of real working module at MPP current candidates are given in (\ref{e3}). Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%. Though procedure of algorithm in \cite{b10}, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}].
%\begin{equation}
%\begin{aligned}
%\textit{$I_{mpp_n}$} = [&\{  \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}   \}, \{ \text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$2_{(11)}$} \},  \\ &\{\text{$0.5_{(9)}$}, \text{$0.5_{(9)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \\ & \{\text{$0.5_{(9)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \{\text{$0.5_{(9)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \\ &\{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$2_{(11)}$} \}, \{\text{$2_{(11)}$}, \text{$2_{(11)}$}, \text{$3_{(4)}$} \}, \\ & \{\text{$2_{(11)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}, \{\text{$3_{(4)}$}, \text{$3_{(4)}$}, \text{$3_{(4)}$} \}] \pm 5\%  \label{e1}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$V_{mpp_n}$} = [&12.4, 24.8, 37.2, 49.6, 62.0, 74.4, 86.8, 99.2, \\&111.6] \pm 18\% \label{e2}
%\end{aligned}
%\end{equation}
%\begin{equation}
%\begin{aligned}
%\textit{$Q_{M_n}$} = [&\{8,8,8\}, \{8,8,8\}, \{4,4,4\}, \{7,7,7\}, \{4,4,4\}, \\&\{2,2,2\}, \{5,5,5\}, \{4,4,4\}, \{2,2,2\}, \{1,1,1\}] \label{e3}
%\end{aligned}
%\end{equation}

 In order to give more precise reconfiguration strategy. Our proposed algorithm firstly sort panels in a particular order for MPP candidates. For the example of fourth MPP candidate \{2, 2, 3\}, by giving dataset in Table \ref{tab1} generate a selection matrix in (\ref{mpp3-1}) that each column indicate panel's number and  each row indicate to string number. Element in the matrix corresponding to number of module which be able to working on string current.
\begin{equation}
%\begin{center}
\begin{tabular}{l|lllllllll}
    & P1 & P2 & P3 & P4 & P5 & P6 & P7 & P8 & P9 \\ \hline
St1 & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
St2 & 1  & 2  & 0  & 2  & 1  & 2  & 2  & 3  & 2  \\
St3 & 0  & 2  & 0  & 0  & 0  & 0  & 1  & 0  & 1 
\end{tabular}\label{mpp3-1}
%\end{center}
\end{equation}
Then calculate number of module difference among string currents. For panel 1, difference between string 3 and string 2 is 1 (\textit{$Diff_1=1$}) and difference between string 2 and string 1 is 0 (\textit{$Diff_2=0$}). Sort panels in lexicographic order by \textit{$Diff_1$} and \textit{$Diff_2$}. As showed in matrix (\ref{sorted}). 
\begin{equation}
\begin{tabular}{l|lllllllll}
        & P2 & P3 & P1 & P5 & P7 & P9 & P4 & P6 & P8 \\ \hline 
St1     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
St2     & 2  & 0  & 1  & 1  & 2  & 2  & 2  & 2  & 3  \\
St3     & 2  & 0  & 0  & 0  & 1  & 1  & 0  & 0  & 0  \\
\textit{$Diff_1$} & 0  & 0  & 1  & 1  & 1  & 1  & 2  & 2  & 3  \\
\textit{$Diff_2$} & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0  & 0 
\end{tabular}\label{sorted}
\end{equation}
To find the best PV configuration, following steps are required:
\begin{enumerate} [1-]
\item Select panels in matrix (\ref{sorted}) from left side to right.
\item If the element in matrix is 0, release corresponding panel
\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. As the example of string 2, selected panels are [Panel 1, Panel 5], these panels contain modules are equal to next unselect panel [Panel 4]. Then swap [Panel 1, Panel 5] and [Panel4], release [Panel 1, Panel 5]. \label{replace}
%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
\item If there remain any unselect panel, set unselect panel to a string with minimum length. 
\end{enumerate}
\subsection{Panel Replace Strategy}
In the section \ref{selection strategy}, to obtain optimal panel selection need swap undesired panel. Based on section \ref{assum}, each panel only contain three identical PV modules. So the element in selection matrix in the range of 0 to 3. The replacement policy follows priorities are:
\begin{enumerate} [ (1) ]
\item Swap a panel contain 3 working modules to \textbf{three} panels each contain 1 working module.
\item Swap a panel contain 3 working modules to \textbf{one} panel contain 1 working module and \textbf{one} contain 2 working modules.
\item Swap a panel contain 2 working modules to \textbf{two} panels each contain 1 working module.
\end{enumerate}

By inspecting the features of each module in Table \ref{tab1}, there are no configuration for MPP candidate 1 and MPP candidate 2. Configuration for MPP candidate 3 is that first string include Panel 1, Panel 2 and Panel 4; the second string include Panel 5, Panel 6 and Panel 7; the third string include Panel 3, Panel 8 and Panel 9. Configuration for MPP candidate 4 is that first string include Panel 1, Panel 5 and Panel 8; the second string include Panel 3, Panel 4 and Panel 6; the third string include Panel 2, Panel 7 and Panel 9. Optimal configuration for this partial-shading PV array as showed in Fig. \ref{reconfiguration}.

\begin{figure}%
    \centering
    \subfloat[MPP candidate 3]{{\includegraphics[width=4cm]{mpp3.png} }}%
%    \qquad
    \subfloat[MPP candidate 4]{{\includegraphics[width=4cm]{mpp4.png} }}%
    \caption{Configuration of partial-shading PV array}%
    \label{reconfiguration}%
\end{figure}

%The general steps of reconfiguration algorithm are presented in Fig. \ref{fig2}. The first step is determine each PV module's \textit{$V_{mpp}$} and \textit{$I_{mpp}$} by using algorithm provided in \cite{b7} \cite{b9}, and calculate MPP current and voltage candidates of PV array. When there are more than two panels connected in series, for a string MPPs is not straightforward. The MPP current and voltage candidates can be evaluated though a procedure presented in \cite{b10}. For string MPP current candidates, \textit{$I_{mpp_n}$} values' different less than 5\% are assumed to be equal. For string MPP voltage candidates, \textit{$V_{mpp_n}$}  can be calculated though multiplay number of active modules (\textit{$N_a$}) by average MPP voltages (\textit{$\bar V_{mpp}$}) with $\pm$18\% error \cite{b10}. Afterward, determine real number of working modules (\textit{$Q_{M_n}$}) for each MPP current candidates by applying method in \cite{b10}. Next, find MPP candidates by multiplying current candidates and voltage candidates which determine by \textit{$Q_{M_n}$}. Due to \textit{$V_{mpp}s$} and \textit{$I_{mpp}s$} can indicate shading distribution among PV array.  Then grouping panels into different shadow distribution.

%After this procedures is conducted for PV array, all panels will be organized into many groups that from un-shadowed or uniform shadow to fully shadowed group. However, if just simply grouping panels by shadow distribution conditions it may cause electrical connection overhead or unable calculate optimal configuration. To further reconfigure PV system into a better configuration, the replacement part of algorithm will proceed as follow:
%\begin{itemize}
%\item Sorting group by different shadow distribution conditions, select panels from first group into a PV string which working on high current level.
%\item If selected panels' working modules ( \textit{$Q_{M_n}^{*}$} ) less than \textit{$Q_{M_n}$} , select panels from next irradiance level group.
%\item If selected panels' \textit{$Q_{M_n}^{*}$} more than \textit{$Q_{M_n}$}, re-select panels to adjust \textit{$Q_{M_n}^{*}$} equal to \textit{$Q_{M_n}$} if it is possible. 
%\end{itemize}
%\begin{figure}[htbp]
%\centerline{\includegraphics[width=6.2cm]{paper-fig3.png}}
%\caption{An example of un-uniform shadowed PV array.}
%\label{fig3}
%\end{figure}

%This algorithm will better understood by applying to shadow condition showed in Fig. \ref{fig3}. This PV system is composed with 9 PV panels connected into 3 strings as showed in Fig.\ref{fig3}. Irradiance levels, \textit{$I_{mpp}$} and \textit{$V_{mpp}$} of each module are given in Table \ref{tab1}.

%\begin{table}[]
%\begin{tabular}{cccc}
%\multicolumn{4}{c}{Data of partial-shading PV array} \\
%\\ \hline \hline
%Panels   & Vmpp(V)  & Impp (A)             & MPP(w)  \\ \hline
%P1       &          & {[}0, 0.5, 2{]}      &         \\
%P2       &          & {[}0.5, 3, 3{]}      &         \\
%P3       &          & {[}0.5, 0.5, 0.5{]}  &         \\
%P4       &          & {[}0, 2, 2{]}        &         \\
%P5       &          & {[}0, 0.5, 2{]}      &         \\
%P6       &          & {[}0.5, 2, 2{]}      &         \\
%P7       &          & {[}0.5, 2, 3{]}      &         \\
%P8       &          & {[}2, 2, 2{]}        &         \\
%P9       &          & {[}0.5, 2, 3{]}      &        
%\end{tabular}
%\end{table}
%The example refer to a three-strings PV array, each string contain with 3 panels, each one made of three identical PV modules (\textit{N}=3). In this example, it is assumed that input range of DC-DC converter and MPPT device defined by \textit{$V_{min}$} = 200V and \textit{$V_{max}$} = 500V.  
%\begin{figure}[htbp]
%\centerline{\includegraphics[width=8cm]{paper-fig4.png}}
%\caption{Organized PV array after first part of Algorithm.}
%\label{fig4}
%\end{figure}
%Due to 5\% error of MPP current candidates and 18\% error of MPP voltage candidates, total error rate of MPP candidates is 23\%. Though procedure of algorithm, MPP candidates with 23\% are: [\{ 0.5, 0.5, 2\}, \{0.5, 2, 2\}, \{2, 2, 2\}, \{2, 2, 3\}] and require working modules per strings are: [\{8, 8, 8\}, \{7, 7, 7\}, \{5, 5, 5\}, \{4, 4, 4\}]. And PV array are organized as Fig.\ref{fig4}
%Those MPP candidates are able to generate maximum output power of PV system, but the configurations of MPP candidates may meet electrical connection overhead. In order to reduce electrical connection simulation time, replacement and feasibility check will be approved. 
%Consider fourth MPP candidate, it require panels on string one working at 2A, panels on string two working at 2A, panels on string three working at 3A and require 4 PV modules working for each string. Firstly, selecting panels for high current string, string three. According to Table \ref{tab1}, only Panel 2, Panel 7 and Panel 9 are able to work at 3A. Those four panel can provide 4 PV module working at 3A and meet requirement of \textit{$Q_{M_n}$}. Because on extra panel can provide module  working on 3A, no replacement will be approved. Means no further improvement for configuration of string three.
%Then select panel for string two, Panel 4 and Panel 8 will be selected, but this configuration is not optimized. Selected panels provide 5 modules able to work at 2A, satisfy requirement of \textit{$Q_{M_n}$} $\ge$ 4, but one module more than requirement. The process will replace Panel 4 by Panel 1 that provide just 4 modules working at 2A. Configuration for string two are Panel 8 and Panel 1. At last, select panels for string one. Panel 4, Panel 5, Panel 6 are selected, they can provide 5 modules working at 2A that satisfy requirement. For configuration on string one due to it is the last string to process and meet requirement, in order to reduce computing time replacement will not be approved. Configuration of MPP candidate \{2, 2, 3\} are \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}. As described in section \ref{assum}, each string have identical length and Panel 3 not been used in any configuration. So optimized configuration for this MPP candidate are: \textit{St} 1:\{Panel 4,Panel 5, Panel 6\}, \textit{St} 2: \{Panel 1, Panel 8, Panel 3\}, \textit{St} 3: \{Panel 2, Panel 7, Panel 9\}. The MPP values of this configuration calculated by multiplay string voltage and current equal to 347.2W are put into evidence.

%For the third MPP candidate, as same calculating procedure as fourth MPP candidate, optimized configuration for MPP candidate \{2, 2, 2\} are: \textit{St} 1:\{Panel 4,Panel 8, Panel 3\}, \textit{St} 2: \{Panel 1, Panel 2, Panel 6\}, \textit{St} 3: \{Panel 5, Panel 7, Panel 9\}. 
%
%The first MPP candidate \{0.5, 0.5, 2\}, after replacement string three contain four panels, \{Panel 4, Panel 8, Panel 1, Panel 2\} but it is over maximum string length of this PV array.
%Also for MPP candidate \{0.5, 2, 2\}, there are no configuration can't provide 7 modules working 
%on three different string at 0.5A, 2A, 2A, respectively.

\section{evaluation of optimization algorithm}
%\subsection{Verification of the Proposed algorithm}
Although the pilot example refers to three strings only, the extension of the method to any number of parallel connected strings is the same.
This section verifies the effectiveness of proposed algorithm using Matlab simulation. With pilot example presented in last section, shading scenario as showed in Fig.\ref{fig5a}. To minimize power loss, the proposed algorithm, as described, is applied to reconfigure the system. The resulting configuration is depicted in Fig.\ref{fig5b} and Fig.\ref{fig5c}. 
%\begin{figure}%
%    \centering
%    \subfloat[label 1]{{\includegraphics[width=5cm]{paper-fig5(a).png} }}
%    \label{fig5a}
%    \qquad
%    \subfloat[label 2]{{\includegraphics[width=5cm]{paper-fig5(b).png} }}%
%    \qquad
%    \subfloat[label 3]{{\includegraphics[width=5cm]{paper-fig5(c).png} }}
%    \caption{3 Figures side by side}%
%    \label{fig5c}%
%\end{figure}
